Untitled Draft

### 2023-01-30 doc/manuscript.Rmd

---
title: "Untitled Draft"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "..")
#setwd("..")
source("R/utils.R")
source("R/model_builder_RQ1.R")
```
```{r load-libraries}
library(targets)
library(gt)
require(ggplot2)
library(papaja)
```

@@

We explored the effects of physical activity on sleep (RQ1) using mixed-effects models. We estimated the effect of physical activity and age

## Model tables

```{r results = "asis"}

tables <- lapply(model_list, function(x) x$table)
sapply(seq_len(length(tables)), function(x){

  cat("## ", names(tables)[x])
  tables[[x]] |> 
    gt() |> 
    apa_style() |> 
    as_raw_html() |> 
    cat()

  cat("\\n")
  cat("\\n")
})

@@

# Discussion

# Conclusion

>>>>

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#setwd("..")
source("R/utils.R")
```

```{r load-libraries}
library(targets)
library(gt)
require(ggplot2)
library(papaja)
```

@@

We explored the effects of physical activity on sleep (RQ1) using mixed-effects models. We estimated the effect of physical activity on sleep by age. The results are presented in Tables \@ref(tab:sleep-by-volume)

```{r sleep-by-volume}
note <- "Adjusted for SES, BMI, and sex. "

format_table <- function(tab){
  tab$term <- gsub("I\\(","", tab$term) |> 
    gsub("_", " ", x = _) |> 
    gsub("\\^2\\)","$^2$", x = _)
  tab
}

model_list$`scale_sleep_duration by scale_pa_volume`$table |> 
  format_table() |> 
  papaja::apa_table(caption = "The quadratic effect of physical activity (volume) on sleep duration by age",
                    note = note,
                    escape = FALSE)

@@
